Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Monch.eps}
    \caption{\textsc{Monch}: Isola E1 Rack 2 Total Power}
    \label{fig:1}
  \end{center}
\end{figure}

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Pilatus.eps}
    \caption{\textsc{Pilatus}: Isola HD Total Power}
    \label{fig:2}
  \end{center}
\end{figure}

@@

In  Figure~\ref{fig:3}, we  compare both  TTS (right  y-axis)  and ETS
(left  y-axis)  metrics  on  both  platforms.  As  expected,  Xeon  E5
outperforms Ivy Bridge EP, being  roughly 1.3x faster.  The reason for
that is  two-fold: (1) it has  higher clock frequency  than Ivy Bridge
(2.6  GHz  against  2.2 GHz),  and  (2)  it  aims at  computing  speed
regardless to  energy consumption.  In our experiments,  Ivy Bridge EP
showed the best energy-to-solution, reducing the energy consumption of
Xeon E5 by approximately $7\%$.

@@

\subsection{Power-performance tracing of \textsc{Cosmo-art}}
\label{subsec:4.3}

@@

\begin{figure*}[htbf]
  \centering
  \scriptsize
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}\\
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}\\
  \caption{1 hour simulation (23h-24h) trace using the MPI blocking
    mode on \textsc{Tintorrum}.}
  \label{fig:11}
\end{figure*}

>>>>

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Monch.eps}
    \caption{\textsc{Monch}: Isola E1 Rack 2 Total Power.}
    \label{fig:1}
  \end{center}
\end{figure}

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Pilatus.eps}
    \caption{\textsc{Pilatus}: Isola HD Total Power.}
    \label{fig:2}
  \end{center}
\end{figure}

@@

In  Figure~\ref{fig:3}, we  compare both  TTS (right  Y-axis)  and ETS
(left  Y-axis)  metrics  on  both  platforms.  As  expected,  Xeon  E5
outperforms Ivy Bridge EP, being  roughly 1.3x faster.  The reason for
that is  two-fold: \emph{i}) it has  higher clock frequency  than Ivy Bridge
(2.6  GHz  against  2.2 GHz),  and  \emph{ii})  it  aims at  computing  speed
regardless to  energy consumption.  In our experiments,  Ivy Bridge EP
showed the best energy-to-solution, reducing the energy consumption of
Xeon E5 by approximately 7\,\%.

@@

\subsection{Power-performance tracing of \cosmoart}
\label{subsec:4.3}

OpenMPI 1.6.5, the communication library tested in \tinto, features two operation modes, 
blocking and modes, which can be selected when the application is launched.
In the polling configuration (the detault mode) ``MPI'' continually polls
the netwrok interface to check for the completion of an event (e.g. send or receive).
This usually yields low latency but high CPU utilization. Thus, can one expcet that this mode attanins the best performance, possibley at the cost a higher energy usage. In the blocking
mode, the CPU is yield to other processes/threads if there are no incoming messages.

@@

\begin{figure*}[htbf]
  \centering
  \scriptsize
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}\\
  \caption{1 hour simulation (23h-24h) trace using the MPI blocking
    mode on \textsc{Tintorrum}.}
  \label{fig:11}
\end{figure*}
